Lifespan analysis

### 2023-07-19 stats/lifespan.Rmd
run lifespan analysis on server

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(Rbeast) # Bayesian change point analysis
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

@@

@@

# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
mdata %>%
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%

@@

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(Rbeast) # Bayesian change point analysis
library(janitor) # clean_names

check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

@@

conditional_effects(mlinear, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T, yaxp = c(0,4,1))

@@

# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
lifespan_plot <- mdata %>%
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%

@@

lifespan_plot

saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
